Classical Simulation of Quantum Error Correction in a Fibonacci Anyon Code

### 2015-06-08 fib2.tex
picture of braiding a loop

\documentclass[aps, prl, letterpaper, twocolumn, superscriptaddress, notitlepage, 10pt]{revtex4-1}
%\documentclass[aps, prl, letterpaper, twocolumn, superscriptaddress, notitlepage, 10pt]{revtex4}
\usepackage{times}

@@

>>>>

%\documentclass[aps, prl, letterpaper, twocolumn, superscriptaddress, notitlepage, 10pt]{revtex4-1}
\documentclass[aps, prl, letterpaper, twocolumn, superscriptaddress, notitlepage, 10pt]{revtex4}
\usepackage{times}

@@

Braiding within an observable will only change the phase
of that observable \dude{???}, otherwise may twist these
loops in various ways:
\begin{align*}
\includegraphics[]{pic-braid-loop.pdf}
\end{align*}
